A practical look at genetic algorithms

### 2015-11-17 evolutionaryComputation/practicals/report.tex
added a todo list

\section{Execution}

>>>>

\paragraph{Bugs found}
Linearly scaled reported the wrong value because it used indeci, so it
gave the first 1 a value of 0, and the second a value of 1 etc.

Trap functions were simply wrongly implemented, instead of counting the
ones they gave positional values of the ones in the block and used the
block as a lookup value for that.
\section{Execution}
%TODO:
% 1. Tournement selection is now implemented wrongly
%	* group(2) to select the first half off the parents
%	* randomly shuffle and group(2) again to select the second half
% 2. Mutation, should be trivial with help of the members factory, decide how
	% many bits will be mutated and then mutate those.
% 3. Offspring generation should create 2 instead of one.
% 4. Experiments
%	Create tables % including:
%		* min pop size for 29 out of 30 runs successful.
%		* The average number of generations
%		* The average CPU time required for running the GA with minimal pop size
%		* average should be over 30 runs
%	Draw a graph from the experiments
%		* pop size on x, # succes on Y
